---
title: ""
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE)
```

# **Lab: The 12 Days of Christmas**

```{r library}
library(english)
library(glue)
library(dplyr)
library(tidyverse)
```

```{r data_read}
xmas <- read.csv("https://www.dropbox.com/s/12ipnczn0fygglt/xmas.csv?dl=1")
xmas2 <- read.csv("https://www.dropbox.com/s/tmilnd6ad8k26wy/xmas2.csv?dl=1")
```

**Introduction**

The song “12 Days of Christmas”, written around 1780, tells the tale of many gifts a person receives in the days leading up to Christmas. (https://en.wikipedia.org/wiki/The_Twelve_Days_of_Christmas_(song))

These gifts repeat and compound; on the first day, the narrator recieves

A partridge in a pear tree.
On the last day, he or she receives

Twelve Drummers Drumming
Eleven Pipers Piping
Ten Lords a Leaping
Nine Ladies Waiting
Eight Maids a Milking
Seven Swans a Swimming
Six Geese a Laying
Five Golden Rings
Four Calling Birds
Three French Hens
Two Turtle Doves
And a Partridge in a Pear Tree

Your task will be to write functions and loop over them to sing the whole song.

**A Test Dataset**

Run the code below to load a dataset called xmas that contains the crucial information about the gifts in the song. We will use this dataset to test out our functions as we work on them.

Remember, though, that future datasets might not have the exact same information as xmas! You’ll want to write your functions to be general; that is, they could be used with any dataset.

xmas <- read.csv("https://www.dropbox.com/s/12ipnczn0fygglt/xmas.csv?dl=1")
Note that your functions can - and should! - reference each other.
That is, don’t duplicate code; use earlier, smaller functions inside your larger functions.


**Step One: Make gift phrases**

```{r make_phrase}
make_phrase <- function(num, gift) {
  num <- english(num)
  return(glue("{num} {gift}"))
}


make_phrase(num = 10, 
            gift = "lords a-leaping")
```

```{r gift_phrase}
xmas <- xmas %>%
  mutate(
    Gift_Phrase = map2_chr(Day, Gift.Item, make_phrase)
  )
```

**Step Two: Verses**

```{r sing_verse}
sing_verse <- function(num, day, gift) {
  seq= seq(num,1,by =-1)
  print(glue::glue("On the {day[num]} day of Christmas, my true love sent to me,"))
  return(map2_chr(seq, gift[seq], make_phrase) %>%
           cat(sep = ", \n"))
}
sing_verse(2, xmas$Day.in.Words, xmas$Gift.Item)
```

**Step Three: Sing the whole song.**

```{r sing_xmas_song_1}
sing_xmas_song <- function(num, day, gift) {
  for (i in num) {
    sing_verse(i,day,gift)
    cat("\n")
  }
}

sing_xmas_song(xmas$Day, xmas$Day.in.Words, xmas$Gift.Item)
```

**Step Four: Try your functions**

Use the following code to load a dataset that is different from the original xmas song. Note that the column names of this dataset are not the same as they were for the original xmas data!

xmas2 <- read.csv("https://www.dropbox.com/s/tmilnd6ad8k26wy/xmas2.csv?dl=1")
Use the function sing_xmas_song() with this dataset to sing a new version of “12 Days of Christmas”.

```{r sing_xmas_song_2}
sing_xmas_song(xmas2$Day, xmas2$Day.in.Words, xmas2$Gift.Item)
```